Data Management for LSST Special Programs

### 2024-03-27 sec_intro.tex
JB comments

The Main Survey will be executed with a set of observing modes, and 
is expected to use alternative standard visits in the $u$-band and 
standard visits in all other bands \citedsp{PSTN-055}.
Different cadences, filter balances, rotational dithers, etc., 
might be applied in the different regions composing Main Survey.
For example, rolling cadence is expected to be implemented in the low-dust 
WFD region only.

Data from the Main Survey will be processed with standard (non-special) processing (Section~\ref{ssec:intro_stdproc}).
This processing will produce, among other data products (LSE-163), 
a contiguous sky footprint that covers at 
least $\sim$18000 deg$^2$ (with $\gtrsim$800 visits per field in WFD regions), 
and is expected to be accomplished with 85--90\% of the observing time.
This contiguous all-sky "deep coadd" may have region-dependent processing parameters and inputs
(e.g., different calibration parameters or deblending algorithms for crowded fields)
and will be of variable depth, as most special regions recieve fewer visits.

@@

Data products from Special Programs is subject to the Rubin Data Policy \citedsp{RDO-013}
in the same way as data products from the Main Survey.

>>>>

The Main Survey will be executed with a set of observing modes, and 
has been recommended by the Survey Cadence Optimization Committee (SCOC)
to use alternative standard visits in the $u$-band;
whether the $grizy$ bands will use alternative or standard visits
remains to be determined \citedsp{PSTN-055}.
Different cadences, filter balances, rotational dithers, etc., 
might be applied in the different regions composing Main Survey.
For example, rolling cadence is expected to be implemented in the low-dust 
WFD region only.

Data from the Main Survey will be processed with standard (non-special) processing (Section~\ref{ssec:intro_stdproc}).
This processing will produce, among other data products (LSE-163), 
a contiguous sky footprint that covers at 
least $\sim$18000 deg$^2$ (with $\gtrsim$800 visits per field in WFD regions), 
and is expected to be accomplished with 85--90\% of the observing time.
This contiguous all-sky "deep coadd" might have region-dependent processing parameters and inputs
where this is determined to be necessary by Rubin Data Management
(e.g., different calibration parameters or deblending algorithms for crowded fields),
and will be of variable depth as most special regions receive fewer visits.
Some depth variation is also expected to come from, e.g., observing conditions and cadence tradeoffs.

@@

Data products from Special Programs are subject to the Rubin Data Policy \citedsp{RDO-013}
in the same way as data products from the Main Survey.
